---
title: "practical ml"
author: "Peter"
date: "February 1, 2020"
output: html_document
pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(caret)
library(randomForest)
library(rpart)
library(rpart.plot)
library(corrplot)
```


```{r}
set.seed(1400)
trainingd <- read.csv("pml-training.csv", na.strings=c("NA","#DIV/0!", ""))
testingd <- read.csv("pml-testing.csv", na.strings=c("NA","#DIV/0!", ""))
```

complete NAs in training data

```{r}
sum(complete.cases(trainingd))
```

then we delete unknown data from columns
```{r}
trainingd <- trainingd[,colSums(is.na(trainingd)) == 0]
testingd <- testingd[,colSums(is.na(testingd)) == 0]
```

we delete columns that we won't use
```{r}
classe <- trainingd$classe

removingcols <- grepl("^X|timestamp|window",names(trainingd))
trainingd <- trainingd[,removingcols]
Cleaneddata <- trainingd[, sapply(trainingd, is.numeric)]
Cleaneddata$classe <- classe

removecols_from_testdata <- grepl("^X|timestamp|window", names(testingd))
testingd <- testingd[,removecols_from_testdata]

Cleanedtdata <- testingd[,sapply(testingd, is.numeric)]
```

we use createDataPartition()func to divide data into 60% for training and 40% for testing
so that we used caret library same as confusionMatrix() func

```{r}
set.seed(60000)
trainda <- createDataPartition(Cleaneddata$classe, p=0.60, list=F)
trainData_w <- Cleaneddata[trainda, ]
testData_w <- Cleaneddata[-trainda, ]
```


we use Random Forest algorithm because it automatically selects
important variables so we fit a predictive model for activity recognition
```{r}
controldata <- trainControl(method = "CV", 7)
modeld <- train(classe ~ ., data=trainData_w, method="rf", trControl=controldata, ntree=300)
##there was error up here package e1071 is required so i do step 25 and try again and it worked fine
#the synatx of download is "install.packages('e1071', dependencies=TRUE)"
modeld
```

we will use **confusionmatrix()** function rn
```{r}
predictprac <- predict(modeld, testData_w)
confusionMatrix(testData_w$classe, predictprac)
```

Then we will calc accuracy for methods and sample errors

```{r}
acc <- postResample(predictprac,testData_w$classe)
acc
```


```{r}
sampleerr <- 1 - as.numeric(confusionMatrix(testData_w$classe, predictprac)$overall[1])
sampleerr
```
acc ~=0.99
sample error ~= 0.000127


then we make a final prediction
```{r}
finalprediction <- predict(modeld, Cleanedtdata, type="prob")
finalprediction
```

final part all about graphics for decision tree and correlation visualization
decision tree:-

```{r}
Decisiontree <- rpart(classe ~ ., data=trainData_w, method="class")
prp(Decisiontree)
```


correlation vis.:-
```{r}
corrp <- cor(trainData_w[,-length(names(trainData_w))])
corrplot(corrp,method="color")
```

